### 2014-05-21 remy_eval.tex
Lowercase section headings
Small fixes

\subsection{Single Bottleneck Results}

@@

%\pagebreak
\subsection{Cellular Wireless Links}

@@

We used Remy to design a congestion-control algorithm to maximize
$-1/\mbox{throughput}$ (minimum potential delay) over these network
parameters, with the degree of multiplexing assumed to have been drawn
uniformly between 1 and 64.

>>>>

\subsection{Single-bottleneck results}

@@

%\pagebreak
\subsection{Cellular wireless links}

@@

We used Remy to design a congestion-control algorithm to maximize
$-\frac{1}{\mbox{\footnotesize throughput}}$ (minimum potential delay) over these network
parameters, with the degree of multiplexing assumed to have been drawn
uniformly between 1 and 64.

### 2014-05-21 sprout_problem.tex
Lowercase section headings
Small fixes

%\section{Cellular Wireless Videoconferencing: Context and Challenges}
\section{Context and Challenges}
\label{sprout:problem}

@@

\subsection{Cellular Networks}

@@

The high delays in cellular wireless networks cannot simply be blamed
on bufferbloat, because there is no single buffer size that will
always work. It is also not simply a question of using an appropriate
Active Queue Management (AQM) scheme, because the difficulties in
picking appropriate parameters are well-documented and become harder
when the available rates change quickly, and such a scheme must be
appropriate when applied to all applications, even if they desire bulk
throughput. In \S\ref{sprout:eval}, we evaluate CoDel~\cite{CoDel}, a
recent AQM technique, together with a modern TCP variant (Cubic, which
is the default in Linux), finding that on more than half of our tested
network paths, CoDel slows down a bulk TCP transfer that has the link
to itself.
%CoDel dramatically improved TCP's
%end-to-end delays compared with a gateway that indefinitely queues
%packets, but not as much as Sprout (even without active queue
%management).
%
%Sprout outperformed Cubic-over-CoDel in delay (with a 60\% reduction)
%but also had 30\% less throughput. Sprout-EWMA surpassed
%Cubic-over-CoDel in throughput (by 31\%) and nearly matched it in
%delay.

@@

\subsection{Measurement Example}

>>>>

%\section{Cellular Wireless Videoconferencing: Context and Challenges}
\section{Context and challenges}
\label{sprout:problem}

@@

\subsection{Cellular networks}

@@

For this reason, the queueing delays in cellular wireless networks cannot simply be blamed
on bufferbloat---there is no single buffer size that will
produce acceptable results across widely varying link conditions. It is also not simply a question of using an appropriate
Active Queue Management (AQM) scheme, because the difficulties in
picking appropriate parameters are well-documented and become harder
when the available rates change quickly, and such a scheme must be
appropriate when applied to all applications, even if they desire bulk
throughput. In \S\ref{sprout:eval}, we evaluate CoDel~\cite{CoDel}, a
recent AQM technique, together with a modern TCP variant (Cubic, which
is the default in Linux), finding that on more than half of our tested
network paths, CoDel slows down a bulk TCP transfer that has the link
to itself.
%CoDel dramatically improved TCP's
%end-to-end delays compared with a gateway that indefinitely queues
%packets, but not as much as Sprout (even without active queue
%management).
%
%Sprout outperformed Cubic-over-CoDel in delay (with a 60\% reduction)
%but also had 30\% less throughput. Sprout-EWMA surpassed
%Cubic-over-CoDel in throughput (by 31\%) and nearly matched it in
%delay.

@@

\subsection{Measurement example}
